Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-10-01 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:10:01	16:14:50	(Thu 1.Oct)

\begin{figure*}[t]\centering
\subfloat[LCA using Kaiser windows, LCA using trigonometric windows, and MVDR. Two lateral image cuts are shown in the leftmost figures, along with the response of a rectangularly weighted DAS. Note how the FWHM of LCA sits in between that of DAS and MVDR. Also note how LCA is insensitive to the window type; its performance is near identical whether it uses Kasier or trigonometric windows.]{\includegraphics[width=\textwidth]{gfx/beamformer_comparison_cross.pdf}%
\label{beamformer_comparison_cross}}
\hfil
\subfloat[Image of Holmengraa. All the adaptive beamformers offer improvement compared to DAS. The shadows are deeper, the edges better refined and the detail level is higher.]{\includegraphics[width=\textwidth]{gfx/beamformer_comparison_holmengraa.pdf}%%
\label{beamformer_comparison_holmengraa}}
\caption{Image quality: Comparing DAS with MVDR and LCA with Kaiser and trigonometric windows.}\label{image_quality}
\end{figure*}

@@

% % \setcounter{dbltopnumber}{1}

@@

We compare LCA image quality to that of DAS and MVDR in \Fig{image_quality}. \Fig{beamformer_comparison_cross} are of the cross, were we display the images computed by LCA using Kaiser windows, LCA using trigonometric windows, and MVDR.

 \Fig{beamformer_comparison_holmengraa}

@@

In comparison, LCA is of O($M N_w$), and extremely well suited for GPUs. Each pixel depends on only a small subset of data, and the windows can be precomputed and stored in GPU cache for near immediate access. Furthermore, since we have observed LCA to perform similarly using other parametric window variants, the complexity can be reduced to near DAS.

@@

\section{Reducing LCA complexity}

>>>>

\begin{figure*}[t]\centering
\subfloat[LCA using Kaiser windows, LCA using trigonometric windows, and MVDR. Two lateral image cuts are shown in the leftmost figures, along with the response of a rectangularly weighted DAS. Note how the FWHM of LCA sits in between that of DAS and MVDR. Also note how LCA is insensitive to the window type; its performance is near identical whether it uses Kasier or trigonometric windows.]{\includegraphics[width=\textwidth]{gfx/beamformer_comparison_cross.pdf}%
\label{beamformer_comparison_cross}}
\hfil
\subfloat[Image of Holmengraa. All the adaptive beamformers offer improvement compared to DAS. The shadows are deeper, the edges better defined and the detail level is higher.]{\includegraphics[width=\textwidth]{gfx/beamformer_comparison_holmengraa.pdf}%%
\label{beamformer_comparison_holmengraa}}
\caption{Image quality: Comparing DAS with MVDR and LCA with Kaiser and trigonometric windows.}\label{image_quality}
\end{figure*}

@@

% % \setcounter{dbltopnumber}{1

@@

We compare LCA image quality to that of DAS and MVDR in \Fig{image_quality}. In \Fig{beamformer_comparison_cross} we display the images computed by LCA using Kaiser windows, LCA using trigonometric windows, and MVDR. Two selected lateral cuts are presented in the left plot. The images and these cuts show that there is minimal difference to using Kaiser windows compared to trigonometric windows. Compared to DAS the LCA produces targets with an FWHM that lies in between that of DAS and MVDR.

In \Fig{beamformer_comparison_holmengraa} we show full sector images of the Holmengraa wreck. We compare the images produced by a Hamming weidted DAS, MVDR and LCA with Kaiser or trigonometric windows. All the adaptive beamformers produce a sharper and less noisy image than DAS, but the difference between LCA and MVDR is minimal. Also here it is nearly impossible to observe any difference to using Kaiser or trigonometric windows with LCA.

@@

In comparison, LCA is of O($M N_\beta N_\phi$), and extremely well suited for GPUs. Each pixel depends on only a small subset of data, and the windows can be precomputed and stored in GPU cache for near immediate access. If we use a trigonometric window function we solve for the window parameter analytically as described in appendix \ref{reducing_lca_complexity}. This reduces the complexity to O($M N_\phi$), and the only remaining LCA parameter is the steering amount.

@@

\section{Reducing LCA complexity}\label{reducing_lca_complexity}
